An examination of the high-order dynamic interactions underlying multi-dimensional timeseries data

### 2018-10-15 paper/main.tex
working on methods section

\documentclass[english]{article}
%\usepackage[utf8]{inputenc}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{babel,blindtext}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{apacite}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage[utf8]{inputenc}
\usepackage{xfrac}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[R]{\thepage}
\usepackage{multirow,booktabs,setspace,caption}
\usepackage{tikz}
\captionsetup[figure]{labelsep=period,labelfont=it,justification=justified,
  singlelinecheck=false,font=doublespacing}
  \usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\lhead{}
\fancyheadoffset[R]{0cm}
\cfoot{}

\fancypagestyle{first page}{
  \lhead{Running head: High-order dynamic interactions}
  \rhead{\thepage}
}

\begin{document}
\title{An examination of the high-order dynamic interactions underlying multi-dimensional timeseries data}
\author{Lucy L. W. Owen$^1$,
Paxton C. Fitzpatrick$^1$,
Kirsten Ziman$^1$,\\
Andrew C. Heusser$^{1,2}$,
Stephen F. Satterthwaite$^1$,
Thomas Hao Chang$^{1,3}$,\\
Qiang Liu$^{1,4}$,
and\
Jeremy R. Manning\textsuperscript{$1, \dagger$}\\
[0.1in]$^1$Department of Psychological and Brain Sciences,\\Dartmouth
College, Hanover, NH\\
$^2$Akili Interactive, Inc, Boston, MA\\
$^3$Amazon.com, Seattle, WA\\
$^4$Department of Computer Science,\\University of Texas at Austin,
Austin, TX\\
\textsuperscript{$\dagger$}Address correspondence to jeremy.r.manning@dartmouth.edu}

\begin{titlepage}
\thispagestyle{fancy}   
% \center
% \vspace*{\fill}
% \huge{}\\[0.5cm]

% \Large{author 1,
% author 2,
% author 3, and
% Jeremy R. Manning\textsuperscript{$\dagger$}}\\[0.5cm]

% \large{Department of Psychological and Brain Sciences, Dartmouth College, Hanover, NH 03755}\\[0.5cm]

% \textsuperscript{$\dagger$} Address correspondence to jeremy.r.manning@dartmouth.edu

% \vspace*{\fill}
\end{titlepage}

% \addtocounter{page}{1}
% \rhead{\thepage}

\maketitle

@@

\begin{align}
\mathrm{corr}_t(x,y) &= \frac{\sum_{t=1}^T \left( x_t - \bar{x_t} \right) \left( y_t - \bar{y_t} \right)}{\sqrt{\sum_{t=1}^{T}\sigma ^{2}_{x_{t}}\sigma ^{2}_{y_{t}}}}\mathrm{, where}\\
\bar{a_t} &= \sum_{t=1}^T w(t)_i a_i\\
\sigma^{2}_{a_t} &= \sum_{t=1}^{T} \left(a_t - \bar{a_t} \right)^2\\
w(t) &= \mathcal{N}\left(1...T ~|~ t, \sigma_\mathcal{N}\right) %update to include eye, laplace, and gaussian weights
\end{align}

@@

\section*{Acknowledgements}
We acknowledge useful discussions with Luke Chang, Hany Farid,
Matthijs van der Meer, and Emily Whitaker. Our work was supported in
part by NSF EPSCoR Award Number 1632738 to J.R.M. and by a sub-award
of DARPA RAM Cooperative Agreement N66001-14-2-4-032 to J.R.M.  The
content is solely the responsibility of the authors and does not
necessarily represent the official views of our supporting
organizations.

>>>>

\documentclass[english]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{apacite}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage[utf8]{inputenc}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage[left]{lineno}
\linenumbers

\title{An examination of the high-order dynamic interactions
  underlying multi-dimensional timeseries data} \author{Lucy
  L. W. Owen$^1$, Thomas Hao Chang$^{1,2}$, and\
  Jeremy R. Manning\textsuperscript{$1, \dagger$}\\
  [0.1in]$^1$Department of Psychological and Brain
  Sciences,\\Dartmouth
  College, Hanover, NH\\
  $^3$Amazon.com, Seattle, WA\\
  \textsuperscript{$\dagger$}Address correspondence to
  jeremy.r.manning@dartmouth.edu}

\begin{document}
\maketitle

@@

\subsection*{Dynamic correlations}
Given a matrix of observations, we can compute the (static)
correlations between any pair of observations, $\mathbf{X}_i$ and
$\mathbf{X}_j$ using:
\begin{align}
  \mathrm{corr}(\mathbf{X}_i, \mathbf{X}_j) &= \frac{\sum_{t=1}^T \left(\mathbf{X}_i(t)
                                              -
                                              \hat{\mathbf{X}_i}\right) \left(\mathbf{X}_j(t)
                                              -
                                              \hat{\mathbf{X}_j}\right)}{\sqrt{\sum_{t=1}^T\left(
                                              \sigma^2_{\mathbf{X}_i}\right) \left(
                                              \sigma^2_{\mathbf{X}_j}\right)}},~\mathrm{where}\\
                                    \hat{\mathbf{X}_k} &= \sum_{t=1}^T
                                                         \mathbf{X}_k(t),~\mathrm{and}\\
  \sigma^2_{\mathbf{X}_k} &= \sum_{t=1}^T \left( \mathbf{X}_k -
                            \hat{\mathbf{X}_k} \right)^2 
\end{align}

We can generalize this formula to compute time-varying correlations by
incorporating a \textit{weight function} that takes a time $t$ as input,
and returns how much the observed data every timepoint (including $t$)
contribute to the correlations at time $t$.
%include figure showing weights (https://github.com/ContextLab/timecorr-paper/issues/1)

\textbf{JRM STOPPED HERE}
\begin{align}
\mathrm{corr}_t(x,y) &= \frac{\sum_{t=1}^T \left( x_t - \bar{x_t} \right) \left( y_t - \bar{y_t} \right)}{\sqrt{\sum_{t=1}^{T}\sigma ^{2}_{x_{t}}\sigma ^{2}_{y_{t}}}}\mathrm{, where}\\
\bar{a_t} &= \sum_{t=1}^T w(t)_i a_i\\
\sigma^{2}_{a_t} &= \sum_{t=1}^{T} \left(a_t - \bar{a_t} \right)^2\\
w(t) &= \mathcal{N}\left(1...T ~|~ t, \sigma_\mathcal{N}\right) %update to include eye, laplace, and gaussian weights
\end{align}

@@

\section*{Acknowledgements}
We acknowledge discussions with Luke Chang, Hany Farid, Paxton
Fitzpatrick, Andrew Heusser, Eshin Jolly, Qiang Liu, Matthijs van der
Meer, Judith Mildner, Gina Notaro, Stephen Satterthwaite, Emily
Whitaker, Weizhen Xie, and Kirsten Ziman. Our work was supported in
part by NSF EPSCoR Award Number 1632738 to J.R.M. and by a sub-award
of DARPA RAM Cooperative Agreement N66001-14-2-4-032 to J.R.M.  The
content is solely the responsibility of the authors and does not
necessarily represent the official views of our supporting
organizations.

\section*{Author contributions}
Concept: J.R.M.  Implementation: T.H.C., L.L.W.O., and
J.R.M.  Analyses: L.L.W.O and J.R.M.
